Making Deep Q-learning Methods Robust to Time Discretization

### 2019-01-23 paper/icml_drau/intro.tex

We focus on near-continuous time because this leads to a clear framework,
but our observations make sense in any setting in which the value
results from a taking a large number of small individual actions. Our
results suggest naive $Q$-learning will fail in such settings without a
delicate balance of hyperparameter scalings.
%the
%advantage of any single individual action is small compared to the total
%return.%, for instance, long time horizon problems.

>>>>

\todo{
We focus on near-continuous time because this leads to a clear framework,
but our observations make sense in any setting in which the value
results from a taking a large number of small individual actions. Our
results suggest naive $Q$-learning will fail in such settings without a
delicate balance of hyperparameter scalings.}
%the
%advantage of any single individual action is small compared to the total
%return.%, for instance, long time horizon problems.
